A separation-of-variable dynamic stiffness matrix method for the free vibration of orthotropic rectangular thin plates

### 2025-07-25 Paper7.tex
Proof-read before resub

	A separation-of-variable dynamic stiffness matrix (SOV-DSM) method is proposed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  

@@

Rectangular plates play an important role in various engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 

@@

Despite being a powerful method for the dynamic analysis of plate assemblies, the FEM requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of Fourier series \cite{williams1995wave,banerjee2015dynamic,liu2016free,liu2024wavenumber,zhou2024wavenumber} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies to arbitrary precision rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to determine all natural frequencies of the fully clamped structure within the interested frequency range, \textit{a priori}.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. 
However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved,liu2022closed}.
To resolve the fully clamped plate problem, Liu and Banerjee \cite{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. 
This idea provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods \cite{liu2024wavenumber,zhou2024wavenumber}. 
However, most solutions applied in these DSM methods are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms might be required to ensure accuracy.

@@

In this study, a separation-of-variable dynamic stiffness matrix (SOV-DSM) method is proposed to avoid solving transcendental eigenvalue equations in SOV methods.
It also fills the gap caused by the limitation of closed-form dynamic stiffness formulations available for existing plate structures.
Firstly, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges based on Rayleigh’s principle. 
This extended SOV solution is then employed to construct dynamic stiffness matrices that accommodate general homogeneous boundary conditions.
By taking advantage of both the SOV and DSM methods, an enhanced W–W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
This enhanced approach resolves the challenge of determining fully clamped frequencies, also called the $J_0$ count problem, a well-known limitation in the application of the W-W algorithm. 
Two types of explicit and closed-form expressions for the $J_0$ term, based on specific supports such as simply supported, guided, or their combinations, are provided to improve the computational efficiency of the eigenvalue problem.
In addition, a novel numerical technique is proposed to compute the mode shape coefficients.

@@

\FloatBarrier
\section{Separation-of-variable dynamic stiffness matrix formulation}\label{sec:SOV-DSM}
In this section, the SOV-DSM formulations for the free vibration analysis of orthotropic rectangular thin plates are developed.  
\Cref{sec:Mathematical model} presents the mathematical model of the extended separation-of-variable method.  
Then, the SOV-DSM formulations in the $x$- and $y$-directions will be proposed separately in \Cref{sec:DSMx} and \Cref{sec:DSMy}, according to the boundary conditions of the plate.

@@

Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:

@@

and from the $\delta \frac{\id \phi}{\id \xi}$ part, the bending moment equilibrium:

@@

Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting 
$k^{v*}_{\xi} \equiv \frac{2a^3 k^v_{\xi}}{D_{11}} $, 
$ k^{r*}_{\eta} \equiv \frac{2a k^r_{\xi}}{D_{11}} $, 
$ S_{\alpha_1} \equiv \sin \alpha_1 $, 
$ C_{\alpha_1} \equiv \cos \alpha_1 $, 
$ Sh_{\beta_1} \equiv \sinh \beta_1$, 
and $ Ch_{\beta_1} \equiv \cosh \beta_1 $, we have:
\begin{equation}\label{eq:ABx}
	&\left[ \begin{array}{c}
		\gamma_1 C_{\alpha_1} - k^{v*}_{\xi=-1} S_{\alpha_1} \\ 
		\gamma_3 S_{\alpha_1} + k^{r*}_{\xi=-1} \alpha_1 C_{\alpha_1} \\ 
		-\gamma_1 C_{\alpha_1} + k^{v*}_{\xi=1} S_{\alpha_1} \\ 
		\gamma_3 S_{\alpha_1} + k^{r*}_{\xi=1} \alpha_1 C_{\alpha_1}
	\end{array} 
	\begin{array}{c}
		\gamma_1 S_{\alpha_1} + k^{v*}_{\xi=-1} C_{\alpha_1} \\ 
		-\gamma_3 C_{\alpha_1} + k^{r*}_{\xi=-1} \alpha_1 S_{\alpha_1} \\ 
		\gamma_1 S_{\alpha_1} + k^{v*}_{\xi=1} C_{\alpha_1} \\ 
		\gamma_3 C_{\alpha_1} - k^{r*}_{\xi=1} \alpha_1 S_{\alpha_1}
	\end{array} 
	\begin{array}{c}
		\gamma_2 Ch_{\beta_1} - k^{v*}_{\xi=-1} Sh_{\beta_1} \\ 
		\gamma_4 Sh_{\beta_1} + k^{r*}_{\xi=-1} \beta_1 Ch_{\beta_1} \\ 
		-\gamma_2 Ch_{\beta_1} + k^{v*}_{\xi=1} Sh_{\beta_1} \\ 
		\gamma_4 Sh_{\beta_1} + k^{r*}_{\xi=1} \beta_1 Ch_{\beta_1}
	\end{array} \right. \\ 
	&\quad
	\left. \begin{array}{c}
		-\gamma_2 Sh_{\beta_1} + k^{v*}_{\xi=-1} Ch_{\beta_1} \\ 
		-\gamma_4 Ch_{\beta_1} - k^{r*}_{\xi=-1} \beta_1 Sh_{\beta_1} \\ 
		-\gamma_2 Sh_{\beta_1} + k^{v*}_{\xi=1} Ch_{\beta_1} \\ 
		\gamma_4 Ch_{\beta_1} + k^{r*}_{\xi=1} \beta_1 Sh_{\beta_1}
	\end{array} \right] \begin{Bmatrix}
		A_1 \\ A_2 \\ A_3 \\ A_4
	\end{Bmatrix} =  \begin{Bmatrix}
		0 \\ 0 \\ 0 \\ 0
	\end{Bmatrix},
or,
\begin{equation}\label{eq:ABx1}
\mathbf{R}_x \mathbf{A} = \mathbf{0},
\begin{equation}\label{eq:gamma}
	&\gamma_1 = -\alpha_1^3 - \chi^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \alpha_1, \\
	&\gamma_2 = \beta_1^3 - \chi^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \beta_1, \\
	&\gamma_3 = -\alpha_1^2 + \frac{\chi^2 D_{12} I_2}{D_{11} I_1}, \\
	&\gamma_4 = \beta_1^2 + \frac{\chi^2 D_{12} I_2}{D_{11} I_1}.
Note that the classic boundary conditions can be obtained by selecting extremely large or small spring stiffness constants.
For non-trivial solutions, the characteristic equation or eigenvalue equation is obtained from the determinant of the matrix $\mathbf{R}_x$ in \Cref{eq:ABx1}, which must be zero.
However, solving these transcendental equations is cumbersome and so the DSM is introduced to avoid such a computation.

@@

Following the same steps as for the \(x\)-direction, the Rayleigh principle is expressed in the form:  
\begin{equation}\label{eq:Rayleighy}
		\delta U &= \omega_y^2 \, \delta T_0,
from which the governing differntial equation in the $y$-direction for $\psi$ is obatained as:
\begin{equation}\label{eq:ODEy}
	\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\chi^2}\left(\frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}J_4}{\chi^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
where $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}}$.
By substituting $\psi(\eta) = B e^{\lambda \eta}$ into \Cref{eq:ODEy}, yields:
\begin{equation}\label{eq:ODEy2}
	\lambda^4 + \frac{2}{\chi^2} \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right) \lambda^2 + \left( \frac{D_{11}J_4}{\chi^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
The solution for $\lambda$ can be expressed as:
\begin{equation}\label{eq:lambda}
	\lambda_{1,2} &= \pm \textit{i} \alpha_2, \qquad \lambda_{3,4} = \pm \beta_2,
\begin{subequations}\label{eq:beta}
	\alpha_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \label{eq:betay1}\\
	\beta_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.\label{eq:betay2}
Similarly, from the shear force and bending moment equilibrium, and by denoting 
$k^{v*}_{\eta} \equiv \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
$ k^{r*}_{\eta} \equiv \frac{2b k^r_{\eta}}{D_{22}} $, 
$S_{\alpha_2}\equiv\sin\alpha_2  $, 
$ C_{\alpha_2}\equiv\cos\alpha_2  $, 
$ Sh_{\beta_2}\equiv\sinh\beta_2$, and 
$Ch_{\beta_2}\equiv \cosh\beta_2$, 
we obtain:
\begin{equation}\label{eq:ABy}
	&\left[ \begin{array}{c}
		\zeta_1C_{\alpha_2}-k^{v*}_{\eta=-1}S_{\alpha_2} \\ \zeta_3S_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2C_{\alpha_2} \\ -\zeta_1C_{\alpha_2}+k^{v*}_{\eta=1}S_{\alpha_2} \\ \zeta_3S_{\alpha_2}+k^{r*}_{\eta=1}\alpha_2C_{\alpha_2}
	\end{array} \begin{array}{c}
		\zeta_1S_{\alpha_2}+k^{v*}_{\eta=-1}C_{\alpha_2} \\ -\zeta_3C_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2S_{\alpha_2} \\ \zeta_1S_{\alpha_2}+k^{v*}_{\eta=1}C_{\alpha_2} \\ \zeta_3C_{\alpha_2}-k^{r*}_{\eta=1}\alpha_2S_{\alpha_2}
	\end{array} \begin{array}{c}
		\zeta_2Ch_{\beta_2}-k^{v*}_{\eta=-1}Sh_{\beta_2} \\ \zeta_4Sh_{\beta_2}+k^{r*}_{\eta=-1}\beta_2Ch_{\beta_2} \\ -\zeta_2Ch_{\beta_2}+k^{v*}_{\eta=1}Sh_{\beta_2} \\ \zeta_4Sh_{\beta_2}+k^{r*}_{\eta=1}\beta_2Ch_{\beta_2}
	\end{array} \right. \\
	&\quad
	\left. \begin{array}{c}
		-\zeta_2Sh_{\beta_2}+k^{v*}_{\eta=-1}Ch_{\beta_2} \\ -\zeta_4Ch_{\beta_2}-k^{r*}_{\eta=-1}\beta_2Sh_{\beta_2} \\ -\zeta_2Sh_{\beta_2}+k^{v*}_{\eta=1}Ch_{\beta_2} \\ \zeta_4Ch_{\beta_2}+k^{r*}_{\eta=1}\beta_2Sh_{\beta_2}
	\end{array} \right]\begin{Bmatrix}
		B_1\\B_2\\B_3\\B_4
	\end{Bmatrix}=\begin{Bmatrix}
		0\\0\\0\\0
	\end{Bmatrix},
or,
\begin{equation}\label{eq:ABy1}
\mathbf{R}_y \mathbf{B} = \mathbf{0},
\begin{equation}\label{eq:gammay}
	&\zeta_1=-\alpha_2^3-\left( \frac{4D_{66}J_3}{\chi^2D_{22}J_1}  - \frac{D_{12}J_2}{\chi^2D_{22}J_1}  \right)\alpha_2,\\
	&\zeta_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\chi^2D_{22}J_1}  - \frac{D_{12}J_2}{\chi^2D_{22}J_1}  \right)\beta_2,\\
	&\zeta_3=-\alpha_2^2+\frac{D_{12}J_2}{\chi^2D_{22}J_1},\\
	&\zeta_4=\beta_2^2+\frac{D_{12}J_2}{\chi^2D_{22}J_1}.
With the help of \Cref{eq:phi_solution2}, the vertical displacement and rotation corresponding to the mode shape $\psi$ along the $y$-direction at the edges $\eta = -1$ and $\eta = 1$ can be expressed as:
\begin{equation}\label{eq:UBy}
	\begin{Bmatrix}
		\psi_{\eta=-1}\\\frac{\id \psi}{\id \eta}_{\eta=-1}\\\psi_{\eta=1}\\\frac{\id \psi}{\id \eta}_{\eta=1}
	\end{Bmatrix}
	= \begin{bmatrix}
		-S_{\alpha_2} & C_{\alpha_2} & -Sh_{\beta_2} & Ch_{\beta_2} \\
		\alpha_2 C_{\alpha_2}/b & \alpha_2 S_{\alpha_2}/b & \beta_2 Ch_{\beta_2}/b & -\beta_2 Sh_{\beta_2}/b \\
		S_{\alpha_2} & C_{\alpha_2} & Sh_{\beta_2} & Ch_{\beta_2} \\
		\alpha_2 C_{\alpha_2}/b & -\frac{\alpha_2 S_{\alpha_2}}{b} & \beta_2 Ch_{\beta_2}/b & \beta_2 Sh_{\beta_2}/b
	\end{bmatrix}
	\begin{Bmatrix}
		B_1\\B_2\\B_3\\B_4
	\end{Bmatrix},		
or,
\begin{equation}\label{eq:UBy1}
\mathbf{\delta}_y= \mathbf{Q}_y\mathbf{B}.
Solving for the eigenvector $\mathbf{B}$, and then substituting into \Cref{eq:ABy1}, we obtain:
\begin{equation}\label{eq:DSM_eqy}
\mathbf{R}_y\mathbf{B}=\mathbf{R}_y \mathbf{Q}_x^{-1} 
\mathbf{\delta}_y = \mathbf{0},
where the dynamic stiffness matrix, denoted as $\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}$, can be obtained from \Cref{eq:DSM_eqy}.
\section*{Remarks}
\addcontentsline{toc}{subsection}{Remarks}
\begin{enumerate}[label=(\roman*)]
	\item For the SOV methods, six independent unknown eigenvalues ($\alpha_1$, $\beta_1$, $\Omega_x$, $\alpha_2$, $\beta_2$, $\Omega_y$) need to be determined for each mode shape $\phi(\xi)\psi(\eta)$.  
	To solve these six variables, four eigenvalue equations are provided in \Cref{eq:alphax1,eq:alphax2,eq:betay1,eq:betay2}, while the remaining two transcendental eigenvalue equations are obtained from the determinants of $\mathbf{R}_x$ in \Cref{eq:ABx1} for the $x$-direction and $\mathbf{R}_y$ in \Cref{eq:ABy1} for the $y$-direction, respectively.
	For classical boundary conditions such as simply supported (S), clamped (C), guided (G), and free (F) edges, these two transcendental equations have been simplified and summarized in previous works \citep{xing2020extended,xing2020improved,xing2022review}.  
	However, the process of selecting appropriate transcendental equations for the existing 55 different boundary-condition combinations remains tedious, and further simplification becomes challenging when non-classical boundary conditions are applied.

>>>>

	A separation-of-variable dynamic stiffness matrix method (SOV-DSM) is proposed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  

@@

Rectangular plates play an important role in many engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 

@@

Despite being a powerful method for the dynamic analysis of plate assemblies, the FEM requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of Fourier series \cite{williams1995wave,banerjee2015dynamic,liu2016free,liu2024wavenumber,zhou2024wavenumber} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} can be applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies to arbitrary precision rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to determine all natural frequencies of the fully clamped structure within the interested frequency range, \textit{a priori}.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. 
However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved,liu2022closed}.
To resolve the fully clamped plate problem, Liu and Banerjee \cite{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. 
This idea provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods \cite{liu2024wavenumber,zhou2024wavenumber}. 
However, most solutions applied in these DSM methods are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms might be required to ensure accuracy.

@@

In this study, a separation-of-variable dynamic stiffness matrix (SOV-DSM) method is proposed to avoid solving transcendental eigenvalue equations in SOV methods.
It also fills the gap caused by the limitation of closed-form dynamic stiffness formulations available for existing plate structures.
Firstly, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges based on Rayleigh’s principle. 
This extended SOV solution is then employed to construct dynamic stiffness matrices that accommodate general homogeneous boundary conditions.
By taking advantage of both the SOV and DSM methods, an enhanced W–W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
This enhanced approach resolves the challenge of determining fully clamped frequencies, also called the $J_0$ count problem, a well-known limitation in the application of the W-W algorithm. 
Two types of explicit and closed-form expressions for the $J_0$ term, based on specific support types such as simply supported, guided, or their combinations, are provided to improve the computational efficiency of the eigenvalue problem.
In addition, a novel numerical technique is proposed to compute the mode shape coefficients.

@@

\FloatBarrier
\section{Separation-of-variable dynamic stiffness matrix formulation}\label{sec:SOV-DSM}
In this section, the SOV-DSM formulations for the free vibration analysis of orthotropic rectangular thin plates are developed.  
\Cref{sec:Mathematical model} presents the mathematical model of the extended separation-of-variable method.  
Then, the SOV-DSM formulations in the $x$- and $y$-directions are developed separately in \Cref{sec:DSMx} and \Cref{sec:DSMy}, according to the boundary conditions of the plate.

@@

Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part of \Cref{eq:Rayleighx2} as:

@@

and from the $\delta \frac{\id \phi}{\id \xi}$ part, the bending moment equilibrium is:

@@

Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting 
$k^{v*}_{\xi} \equiv \frac{2a^3 k^v_{\xi}}{D_{11}} $, 
$ k^{r*}_{\eta} \equiv \frac{2a k^r_{\xi}}{D_{11}} $, 
$ S_{\alpha_1} \equiv \sin \alpha_1 $, 
$ C_{\alpha_1} \equiv \cos \alpha_1 $, 
$ Sh_{\beta_1} \equiv \sinh \beta_1$, 
and $ Ch_{\beta_1} \equiv \cosh \beta_1 $, we have:
%
\begin{equation}\label{eq:ABx}
\begin{split}
	&\left[ \begin{array}{c}
		\gamma_1 C_{\alpha_1} - k^{v*}_{\xi=-1} S_{\alpha_1} \\ 
		\gamma_3 S_{\alpha_1} + k^{r*}_{\xi=-1} \alpha_1 C_{\alpha_1} \\ 
		-\gamma_1 C_{\alpha_1} + k^{v*}_{\xi=1} S_{\alpha_1} \\ 
		\gamma_3 S_{\alpha_1} + k^{r*}_{\xi=1} \alpha_1 C_{\alpha_1}
	\end{array} 
	\begin{array}{c}
		\gamma_1 S_{\alpha_1} + k^{v*}_{\xi=-1} C_{\alpha_1} \\ 
		-\gamma_3 C_{\alpha_1} + k^{r*}_{\xi=-1} \alpha_1 S_{\alpha_1} \\ 
		\gamma_1 S_{\alpha_1} + k^{v*}_{\xi=1} C_{\alpha_1} \\ 
		\gamma_3 C_{\alpha_1} - k^{r*}_{\xi=1} \alpha_1 S_{\alpha_1}
	\end{array} 
	\begin{array}{c}
		\gamma_2 Ch_{\beta_1} - k^{v*}_{\xi=-1} Sh_{\beta_1} \\ 
		\gamma_4 Sh_{\beta_1} + k^{r*}_{\xi=-1} \beta_1 Ch_{\beta_1} \\ 
		-\gamma_2 Ch_{\beta_1} + k^{v*}_{\xi=1} Sh_{\beta_1} \\ 
		\gamma_4 Sh_{\beta_1} + k^{r*}_{\xi=1} \beta_1 Ch_{\beta_1}
	\end{array} \right. \\ 
	&\quad
	\left. \begin{array}{c}
		-\gamma_2 Sh_{\beta_1} + k^{v*}_{\xi=-1} Ch_{\beta_1} \\ 
		-\gamma_4 Ch_{\beta_1} - k^{r*}_{\xi=-1} \beta_1 Sh_{\beta_1} \\ 
		-\gamma_2 Sh_{\beta_1} + k^{v*}_{\xi=1} Ch_{\beta_1} \\ 
		\gamma_4 Ch_{\beta_1} + k^{r*}_{\xi=1} \beta_1 Sh_{\beta_1}
	\end{array} \right] \begin{Bmatrix}
		A_1 \\ A_2 \\ A_3 \\ A_4
	\end{Bmatrix} =  \begin{Bmatrix}
		0 \\ 0 \\ 0 \\ 0
	\end{Bmatrix},
\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:ABx1}
\mathbf{R}_x \mathbf{A} = \mathbf{0},
\end{equation}
%
where,
%
\begin{equation}\label{eq:gamma}
\begin{split}
	&\gamma_1 = -\alpha_1^3 - \chi^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \alpha_1, \\
	&\gamma_2 = \beta_1^3 - \chi^2 \left( \frac{4D_{66}S_3}{D_{11}I_1} - \frac{D_{12}I_2}{D_{11}I_1} \right) \beta_1, \\
	&\gamma_3 = -\alpha_1^2 + \frac{\chi^2 D_{12} I_2}{D_{11} I_1}, \\
	&\gamma_4 = \beta_1^2 + \frac{\chi^2 D_{12} I_2}{D_{11} I_1}.
\end{split}
\end{equation}

Note that the classic boundary conditions can be obtained by selecting extremely large or small spring stiffness constants.
For non-trivial solutions, the characteristic equation or eigenvalue equation is obtained from the determinant of the matrix $\mathbf{R}_x$ in \Cref{eq:ABx1}, which must be zero.
However, solving these transcendental equations is cumbersome and so the DSM is introduced to avoid such a computation.

@@

Following the same steps as for the \(x\)-direction, the Rayleigh principle is expressed in the form:  
%
\begin{equation}\label{eq:Rayleighy}
	\begin{split}
		\delta U &= \omega_y^2 \, \delta T_0,
	\end{split}
\end{equation}
%
from which the governing differntial equation in the $y$-direction for $\psi$ is obatained as:
%
\begin{equation}\label{eq:ODEy}
	\frac{\id^4 \psi}{\id \eta^4} + \frac{2}{\chi^2}\left(\frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1}\right)\frac{\id^2 \psi}{\id \eta^2} + \left( \frac{D_{11}J_4}{\chi^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) \psi = 0,
\end{equation}
%
where $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}}$.
By substituting $\psi(\eta) = B e^{\lambda \eta}$ into \Cref{eq:ODEy}, we get:
%
\begin{equation}\label{eq:ODEy2}
\begin{split}
	\lambda^4 + \frac{2}{\chi^2} \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right) \lambda^2 + \left( \frac{D_{11}J_4}{\chi^4D_{22}J_1} - \frac{b^4D_{11}}{D_{22}} \Omega_y^4 \right) = 0.
\end{split}
\end{equation}
%
The solution for $\lambda$ can be expressed as:
%
\begin{equation}\label{eq:lambda}
\begin{split}
	\lambda_{1,2} &= \pm \textit{i} \alpha_2, \qquad \lambda_{3,4} = \pm \beta_2,
\end{split}
\end{equation}
%
where,
%
\begin{subequations}\label{eq:beta}
\begin{align}
	\alpha_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2\frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } + \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1}}, \label{eq:betay1}\\
	\beta_2 &= \frac{1}{\chi} \sqrt{ \sqrt{ \left( \frac{D_{12}J_2}{D_{22}J_1} - 2 \frac{D_{66}J_3}{D_{22}J_1} \right)^2 - \frac{D_{11}J_4}{D_{22}J_1} + \frac{a^4 D_{11}}{D_{22}} \Omega_y^4 } - \frac{D_{12}J_2}{D_{22}J_1} + 2 \frac{D_{66}J_3}{D_{22}J_1}}.\label{eq:betay2}
\end{align}
\end{subequations}

Similarly to the $x$-direction, from the shear force and bending moment equilibrium, and by denoting 
$k^{v*}_{\eta} \equiv \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
$ k^{r*}_{\eta} \equiv \frac{2b k^r_{\eta}}{D_{22}} $, 
$S_{\alpha_2}\equiv\sin\alpha_2  $, 
$ C_{\alpha_2}\equiv\cos\alpha_2  $, 
$ Sh_{\beta_2}\equiv\sinh\beta_2$, and 
$Ch_{\beta_2}\equiv \cosh\beta_2$, 
we obtain:
%
\begin{equation}\label{eq:ABy}
\begin{split}
	&\left[ \begin{array}{c}
		\zeta_1C_{\alpha_2}-k^{v*}_{\eta=-1}S_{\alpha_2} \\ \zeta_3S_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2C_{\alpha_2} \\ -\zeta_1C_{\alpha_2}+k^{v*}_{\eta=1}S_{\alpha_2} \\ \zeta_3S_{\alpha_2}+k^{r*}_{\eta=1}\alpha_2C_{\alpha_2}
	\end{array} \begin{array}{c}
		\zeta_1S_{\alpha_2}+k^{v*}_{\eta=-1}C_{\alpha_2} \\ -\zeta_3C_{\alpha_2}+k^{r*}_{\eta=-1}\alpha_2S_{\alpha_2} \\ \zeta_1S_{\alpha_2}+k^{v*}_{\eta=1}C_{\alpha_2} \\ \zeta_3C_{\alpha_2}-k^{r*}_{\eta=1}\alpha_2S_{\alpha_2}
	\end{array} \begin{array}{c}
		\zeta_2Ch_{\beta_2}-k^{v*}_{\eta=-1}Sh_{\beta_2} \\ \zeta_4Sh_{\beta_2}+k^{r*}_{\eta=-1}\beta_2Ch_{\beta_2} \\ -\zeta_2Ch_{\beta_2}+k^{v*}_{\eta=1}Sh_{\beta_2} \\ \zeta_4Sh_{\beta_2}+k^{r*}_{\eta=1}\beta_2Ch_{\beta_2}
	\end{array} \right. \\
	&\quad
	\left. \begin{array}{c}
		-\zeta_2Sh_{\beta_2}+k^{v*}_{\eta=-1}Ch_{\beta_2} \\ -\zeta_4Ch_{\beta_2}-k^{r*}_{\eta=-1}\beta_2Sh_{\beta_2} \\ -\zeta_2Sh_{\beta_2}+k^{v*}_{\eta=1}Ch_{\beta_2} \\ \zeta_4Ch_{\beta_2}+k^{r*}_{\eta=1}\beta_2Sh_{\beta_2}
	\end{array} \right]\begin{Bmatrix}
		B_1\\B_2\\B_3\\B_4
	\end{Bmatrix}=\begin{Bmatrix}
		0\\0\\0\\0
	\end{Bmatrix},
\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:ABy1}
\mathbf{R}_y \mathbf{B} = \mathbf{0},
\end{equation}
%
where,
%
\begin{equation}\label{eq:gammay}
\begin{split}
	&\zeta_1=-\alpha_2^3-\left( \frac{4D_{66}J_3}{\chi^2D_{22}J_1}  - \frac{D_{12}J_2}{\chi^2D_{22}J_1}  \right)\alpha_2,\\
	&\zeta_2=\beta_2^3-\left( \frac{4D_{66}T_3}{\chi^2D_{22}J_1}  - \frac{D_{12}J_2}{\chi^2D_{22}J_1}  \right)\beta_2,\\
	&\zeta_3=-\alpha_2^2+\frac{D_{12}J_2}{\chi^2D_{22}J_1},\\
	&\zeta_4=\beta_2^2+\frac{D_{12}J_2}{\chi^2D_{22}J_1}.
\end{split}
\end{equation}

With the help of \Cref{eq:phi_solution2}, the vertical displacement and rotation corresponding to the mode shape $\psi$ along the $y$-direction at the edges $\eta = -1$ and $\eta = 1$ can then be expressed as:
%
\begin{equation}\label{eq:UBy}
\begin{split}
	\begin{Bmatrix}
		\psi_{\eta=-1}\\\frac{\id \psi}{\id \eta}_{\eta=-1}\\\psi_{\eta=1}\\\frac{\id \psi}{\id \eta}_{\eta=1}
	\end{Bmatrix}
	= \begin{bmatrix}
		-S_{\alpha_2} & C_{\alpha_2} & -Sh_{\beta_2} & Ch_{\beta_2} \\
		\alpha_2 C_{\alpha_2}/b & \alpha_2 S_{\alpha_2}/b & \beta_2 Ch_{\beta_2}/b & -\beta_2 Sh_{\beta_2}/b \\
		S_{\alpha_2} & C_{\alpha_2} & Sh_{\beta_2} & Ch_{\beta_2} \\
		\alpha_2 C_{\alpha_2}/b & -\frac{\alpha_2 S_{\alpha_2}}{b} & \beta_2 Ch_{\beta_2}/b & \beta_2 Sh_{\beta_2}/b
	\end{bmatrix}
	\begin{Bmatrix}
		B_1\\B_2\\B_3\\B_4
	\end{Bmatrix},		
\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:UBy1}
\mathbf{\delta}_y= \mathbf{Q}_y\mathbf{B}.
\end{equation}
%
Solving for the eigenvector $\mathbf{B}$, and then substituting into \Cref{eq:ABy1}, we obtain:
%
\begin{equation}\label{eq:DSM_eqy}
\mathbf{R}_y\mathbf{B}=\mathbf{R}_y \mathbf{Q}_x^{-1} 
\mathbf{\delta}_y = \mathbf{0},
\end{equation}
%
where the dynamic stiffness matrix, denoted as $\mathbf{K}_y = \mathbf{R}_y \mathbf{Q}_y^{-1}$, can be obtained from \Cref{eq:DSM_eqy}.
